\include{global/preamble}

%\usecolortheme[RGB={200,200,200}]{structure}

\subtitle[Module D]{{\large Module D: Simulations and Application Frameworks}\\*[0.3em]Homework 1: Get started with the Einstein Toolkit}
\author[Peter Diener]{Dr Peter Diener}
\date{November 15, 2013}
\usecolortheme[RGB={45,160,140}]{structure}

\begin{document}

\frame{\titlepage}

\section{Homework}
\frame{\frametitle{}\begin{centering}\LARGE\insertsectionhead\\\end{centering}}

\frame[containsverbatim]{ \frametitle{Homework}
  Your homework for this week will be to checkout (using GetComponents) the 
  Einstein Toolkit, compile and run a simulation on Super Mike II (using
  Simfactory).
  You should (mostly) follow the tutorial at:
  {\small \tt{https://docs.einsteintoolkit.org/et-docs/Tutorial\_for\_New\_Users}}
  \vspace{0.5em}

  As this tutorial was written for the machine Queen Bee, there is a few 
  differences in setting up Simfactory so the tutorial has to be modified
  as follows:
  \vspace{0.5em}

  Log into {\tt mike.hpc.lsu.edu} and start following the tutorial in
  your home directory with the following modifications.
  \begin{itemize}
    \item The {\tt git}, {\tt python} and {\tt svn} clients are already 
	  available so skip the commands:\\
	  {\tt soft add +python-2.6.4-gcc-4.3.2} \\
          {\tt soft add +git} \\
	  {\tt soft add +subversion-1.8.3-gcc-4.3.2}
  \end{itemize}
}

\frame[containsverbatim]{ \frametitle{Homework}
  \begin{itemize}
    \item When you get to the section ``Configure the Simulation Factory'':
	  replace the first command {\tt mkdir scratch/simulations} with \\
	  {\tt mkdir /work/<username>/simulations}. Here, replace ``username''
	  with your username on Mike.
    \item Execute the next two commands. 
    \item When asked to edit the file 
	  {\tt simfactory/etc/defs.local.ini}: change ``YOUR\_LOGIN'', 
	  ``YOUR@EMAIL.ADDRESS'' and ``YOUR\_THORNLIST'' as described but
	  skip changing ``YOUR\_ALLOCATION'' and instead add a mike specific
          section at the end of the file containing:
	  \begin{verbatim}
[mike]
allocation      = hpc_startup_<username>
sourcebasedir   = /home/<username>
	  \end{verbatim}
  \end{itemize}
} 

\frame[containsverbatim]{ \frametitle{Homework}
  \begin{itemize}
    \item Continue with the tutorial (i.e.\ compile and running) and wait
          until the run has finished before continuing.
    \item When you get to the ``Look at Results'' part of the tutorial:
      Log into Mike (of course) instead of Queen Bee (don't forget forwarding of X). \\
      To change to the output directory do:\\
	{\footnotesize {\tt cd /work/<username>/simulations/static\_tov/output-0000/static\_tov}}
    \item Do not continue with the additional examples.
  \end{itemize}
  Your homework will consist of the standard output from the
  simulation as well as your versions of the gnuplot plots. \\
  Commit the standard output file located in\\
   {\footnotesize {\tt /work/<username>/simulations/static\_tov/output-0000/static\_tov.out}}\\
  and postscript or pdf files with the plots to {\tt coursework/D2/}
  in your personal subversion repository for CSC7700. \\
 Due date: November 22, 2013.
}
\end{document}
